The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-03 paper.tex
update

Early attempts to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
assumed that the jet is vertial to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to the plane of the disc.\
A number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

To this end, this work introduces a dense thin disk of interstellar medium\
around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\
The thin disk contains a reservoir of dense molecular/atomic gas, resulting in\

@@

\section{Conclusions}
\label{Conclusions}

>>>>

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
assumed that the jet is vertial to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to the plane of the disc.\
A number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

To this end, this work introduces a dense thin disk of interstellar medium\
around a jet source to deflects and decelerates the jets,\
in an attempt to remedy the symmetry problem of the Galactic bubbles.\

@@

\section{Conclusions}
\label{Conclusions}
We have found qualitative similarities between the results our simulations\
and the observed spectrum and morphological structure of the Galactic bubbles.

Since the jets encounter a larger column depth of cloudsalong their path,\
they interact more strongly with the dense ISM.\
The jets do not immediately clear a channel along the inclined axis of launch.\
Rather, the dense clouds deflect the jets, which then decelerate\
and launch a sub-relativistic outflow along the minor axis following the path of least resistance.
